---
title: |
  CSI 702 course materials
  <img src="img/course-logo-semester-square-section-003.svg" align="right" height=150>
date: Spring 2019 semester
output: github_document
---

```{r setup, include = FALSE}
source("../R/rmarkdown_setup.R")
options(knitr.kable.NA = "")
schedule <- readr::read_csv("../data/schedule.csv")
homeworks <- readr::read_csv("../data/homeworks.csv")
final_project <- readr::read_csv("../data/final_project.csv")
software <- readr::read_csv("../data/software.csv")
```

*   [Syllabus](#syllabus)
*   [Schedule](#schedule)
*   [Homeworks](#homeworks)
*   [Final project](#final-project)
*   [Resources and links](#resources-and-links)
    *   [Software](#software)
*   [License](#license)

## Syllabus

The syllabus is available as a Google Doc: https://docs.google.com/document/d/14qsCAP9Dei89EobiOC-nGDpM-ER4hlDY9fGw-Ylau3k

## Schedule

```{r schedule, echo = FALSE}
knitr::kable(
  x = schedule,
  format = "pandoc",
)
```

## Homeworks

```{r homeworks, echo = FALSE}
knitr::kable(
  x = homeworks,
  format = "pandoc",
  align = "rll"
)
```

## Final project

```{r final-project, echo = FALSE}
knitr::kable(
  x = final_project,
  format = "pandoc"
)
```

## Resources and links

### Software

```{r software, echo = FALSE, results = 'asis'}
knitr::kable(
  x = software,
  format = "html",
  escape = FALSE
)
```

## License

[![Creative Commons License][cc-by-sa-4-img]][cc-by-sa-4]

Unless otherwise noted, the course materials in this repository are licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License][cc-by-sa-4].

[cc-by-sa-4]:                http://creativecommons.org/licenses/by-sa/4.0/
[cc-by-sa-4-img]:            https://i.creativecommons.org/l/by-sa/4.0/88x31.png
